Pillar 2 - Topic Modeling

### 2019-03-19 Pillar 2 - Topic Modeling.Rmd
Extracting and Plotting Functions for models

We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`
```{r LDA fit, cache = TRUE, eval = TRUE}
topic_model <- tibble(

  n_topic = seq(from = 5, to = 250, by = 5)

  ) %>%

  mutate(
    TM_overview = n_topic %>% map( .f = my_LDA, corpus = d_cast$overview),
    TM_manual   = n_topic %>% map( .f = my_LDA, corpus = d_cast$manuals)
  )
```
#DELETE LATERRRRRR- HELPER IMPORT
```{r}
load("Output/topic_model.RDATA")
```

##Model Evaluation
###Perplexity
Perplexity is a measure of how well a probability model predicts a sample. (Thus may want to do cross validation.) 
```{r perplexity function, eval = TRUE}

@@

#Get perplexity
test_perplexity <- topic_model %>%
  mutate(perplex_overview = map(.x = TM_overview, .f = my_perplexity, d_cast$overview),
         perplex_manual   = map(.x = TM_manual,   .f = my_perplexity, d_cast$manual))
```

###log_likelihood
```{r log likelihood, eval = TRUE}
#Log likelihood:
test_likelihood <- topic_model %>% mutate(logLik_overview = map(.x = TM_overview, .f = logLik),
                                         logLik_manual   = map(.x = TM_manual,   .f = logLik))

@@

###Plots
```{r perplexity plots, eval = TRUE}
#perplexity
plot(test_perplexity$n_topic, test_perplexity$perplex_overview)
plot(test_perplexity$n_topic, test_perplexity$perplex_manual)

#log likelihood
plot(test_likelihood$n_topic, test_likelihood$logLik_overview)
plot(test_likelihood$n_topic, test_likelihood$logLik_manual)
```

##Get Beta/Gamma functions
```{r getting gamma and beta, eval = TRUE}
get_beta <- function(results){

  tidy(results, matrix = "beta")           %>%
    mutate(topic = paste("Topic", topic) ) %>%
      arrange(topic, desc(beta) )

@@

get_gamma <- function(results){

  tidy(results, matrix = "gamma")          %>%
    mutate(topic = paste("Topic", topic) ) %>%
      arrange(topic, desc(gamma) )
}

@@

>>>>

We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`
##Functions for models (get gamma, get beta, extract_dtm)
```{r getting gamma and beta, eval = TRUE}
#extract dtm
extract_dtm <- function(wt) d_cast[[wt]]

# #get beta
# get_beta <- function(results){
#   
#   tidy(results, matrix = "beta")           %>%
#     mutate(topic = paste("Topic", topic) ) %>%
#       arrange(topic, desc(beta) )
#   
# }
# 
# #get gamma
# get_gamma <- function(results){
#   
#   tidy(results, matrix = "gamma")          %>%
#     mutate(topic = paste("Topic", topic) ) %>%
#       arrange(topic, desc(gamma) )
# }

get_distributions <- function(model, distrib_str){ #input gamma or beta
  tidy(model, matrix = distrib_str)        %>%
    mutate(topic = paste("Topic", topic) ) %>%
      arrange(topic, desc(!!sym(distrib_str)))
}

@@

my_logLik <-  function (model)

@@

```{r LDA fit, cache = TRUE, eval = TRUE}

test_topic_model <- tibble( #change to topic_model
  #repeat each topic number twice
  n_topic = rep(seq(from = 2, to = 4, by = 1), each = 2) # from = 5, to = 250, by = 5

  ) %>%
  mutate(Origin     = rep(c("overview", "manuals"), 3),         # should be 50
         `Topic ID` = paste(Origin, n_topic, sep = "_"),
         DTM        = pmap(.l = list(Origin), .f = extract_dtm),

         #fit model
         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control_fast),

         #Gamma distribution
         Gamma = pmap(.l = list(Model), .f = get_distributions, distrib_str = "gamma"),

         #Beta distribution
         Beta = pmap(.l = list(Model),  .f = get_distributions, distrib_str = "beta"),

         #Perplexity
         Perplexity = pmap_dbl(.l = list(Model, DTM), .f = my_perplexity),

         #Loglikelihood
         LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik) #this removes the degrees of freedom data
         )

```
#DELETE LATERRRRRR- HELPER IMPORT
```{r}
load("Output/topic_model.RDATA")
```

##Model Evaluation
###Plots
```{r perplexity plots, eval = TRUE}
#plot evaluation
plot_evaluation <- function(){

  #data
  test_topic_model %>%

    #Wrangling
    select(n_topic, Origin, Perplexity, LogLikelihood) %>%

    gather(key = "Eval Type", value = "Eval Value", c(Perplexity, LogLikelihood)) %>%

    #Graphics
    ggplot(mapping = aes(x = n_topic, y = `Eval Value`)) +
    geom_point() +
    facet_wrap(`Eval Type` ~ Origin, scales = "free") +
    theme_minimal()

@@

plot_evaluation()
```

@@

extract_overview <- function() topic_model_gb %>% filter(n_topic == n_topics_overview)
extract_manual   <- function() topic_model_gb %>% filter(n_topic == n_topics_manual  )

df %>% mutate(var_new = list(var_old1, var_old2) %>% pmap(my_function))

data <- tribble(
  ~ ID,
  "overview",
  "manual"
  ) %>%
  mutate(df = if_else(ID == "overview", extract_overview(), extract_manual))
